Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-25 paper/paper.tex
#25 clarify equation 2 explanation

For clarity I move from the event study to a basic difference-in-differences specification; this way there is only a single coefficient of interest. I simply replace the lead and lag dummies with the post-treatment indicator $\mathbf{1}(t \ge e^{NewState}_i)$. Also, this equation features a vector of city-year level control variables $\mathbf{X}_{it}$. In the baseline version of this specification I control only for the dummy $\mathbf{1}(S_{it} > 0)$ that indicates switches in the same period, exactly like in Equation \eqref{eq:sw22}. In a robustness check I will additionally control for conflict incidents.

>>>>

For clarity I move from the event study to a basic difference-in-differences specification; this way there is only a single coefficient of interest. I simply replace the lead and lag dummies with the post-treatment indicator $\mathbf{1}(t \ge e^{NewState}_i)$. Another minor change is that this equation features a vector of city-year level control variables $\mathbf{X}_{it}$ --- however, in the baseline version of this specification I control only for the dummy $\mathbf{1}(S_{it} > 0)$ that indicates switches in the same period, exactly like in Equation \eqref{eq:sw22}. In a robustness check I will additionally control for conflict incidents.
